---
title: "MATH 214: Homework 02"
author: "Write Your Name Here"
date: "Due Wednesday 2015/3/4 5:00pm on Moodle"
output: html_document
---

```{r, echo=FALSE}
suppressPackageStartupMessages(library(foreign))
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(ggplot2))
```



## Question 1:

Question 4 on page 76 from Chapter 4 of Data Analysis Using Regression and Multilevel/Hierarchical Models.  The codebook can be found [here](http://www.stat.columbia.edu/~gelman/arm/examples/pollution/pollution.txt).  


```{r, echo=FALSE}
url <- "http://www.stat.columbia.edu/~gelman/arm/examples/pollution/pollution.dta"
pollution <- read.dta(url) %>% tbl_df()
```



## Question 2:

I actually prefer flying on older planes.  Even though they aren't as nice, they tend to have more room.  Which airlines should I favor?

```{r}

```



## Question 3:

* What states did listed Southwest Airlines flights tend to fly to?
* What states did all Southwest Airlines flights tend to fly to?

```{r}

```



## Question 4:

What weather patterns are associated with the biggest departure delays?

```{r}

```



## Question 5:

I want to know what proportionately regions (NE, south, west, midwest) each carrier flies to from Houston in the month of July.  Consider the `lubridate` package.

```{r}

```



## Question 6:

Get creative:  Answer one question of your own using this data.  The more interesting the question the better.

```{r}

```
