---
title: "MATH 214: Homework 02"
author: "Write Your Name Here"
date: "Due Friday 2015/3/20 5:00pm on Moodle"
output: html_document
---

Note:  For all R code chucks (grey blocks below where insert R code) I've set `echo=FALSE` so that R commands won't be echoed.  I'll look at the R code separately from the report


```{r, echo=FALSE}
suppressPackageStartupMessages(library(dplyr))
jukebox <- read.csv("jukebox.csv", header=TRUE)
```



## Question 1:

For each academic year between 2003-2004 thru 2008-2009, who were the top 10 artists played?  Define

* the start of academic year as the first Tuesday in September
* the end of the academic year as the first Monday in January plus 15 weeks plus 4 days (i.e. the Friday of that week)

Display the results in easily digestible format.  

```{r, echo=FALSE}
```



## Question 2:

Plot a time series of the number of songs played each week.  What patterns do you observe?  

```{r, echo=FALSE}
```



## Question 3:

Compare Eminem, Talking Heads, and Girl Talk's popularity over the this time period.

```{r, echo=FALSE}
```



## Question 4:

Did jukebox using Reedies' taste in songs change much during the period of the Sunday night blues?  Define this period to be between 4pm and 11pm.  

```{r, echo=FALSE}
```



## Question 5:

Choose your own question to evaluate about the jukebox.  

```{r, echo=FALSE}
```






