---
title: "MATH 214: Homework 02"
author: "Write Your Name Here"
date: "Due Friday 2015/3/20 5:00pm on Moodle"
output: html_document
---

Note:  For all R code chucks (grey blocks below where insert R code) I've set `echo=FALSE` so that R commands won't be echoed.  I'll look at the R code separately from the report


```{r, echo=FALSE}
suppressPackageStartupMessages(library(dplyr))
jukebox <- read.csv("jukebox.csv", header=TRUE)
```



## Question 1:

For each academic year between 2003-2004 thru 2008-2009, who were the top 10 artists played?  Define

* the start of academic year as the first Tuesday in September
* the end of the academic year as the first Monday in January plus 15 weeks plus 4 days (i.e. the Friday of that week)

You can find these dates manually, or with the help of lubridate functions, or entirely using lubrdiate functions.  Display the results in easily digestible format.  

```{r, echo=FALSE}
```



## Question 2:

Plot a time series of the number of songs played each week.  What patterns do you observe?  

```{r, echo=FALSE}
```



## Question 3:

Compare Eminem, Talking Heads, and Girl Talk's month by month popularity over this time period.

```{r, echo=FALSE}
```



## Question 4:

Did jukebox using Reedies' taste in songs change much during the period of the Sunday night blues?  Define this period to be between 4pm and 11pm on Sundays.  

```{r, echo=FALSE}
```



## Question 5:

We want to study the volatility of bitcoin prices.  Let our measure of volatility be the relative change from day-to-day in price.  For which periods since 2013/01/01 did we see the most volatility?

```{r, echo=FALSE}
```



## Question 5:

Compare the volatility of bitcoin prices with the volatility of the price of gold for the same time period.  What do you observe?  

```{r, echo=FALSE}
```



## Question 7:

Answer another question of interest to you about the jukebox data.  

```{r, echo=FALSE}
```



## Question 8:

Answer another question of interest to you using the data on Quandl.  Preferably on a topic you are interested in.  

```{r, echo=FALSE}
```






