---
title: "MATH 214: Homework 01"
author: "Write Your Name Here"
date: "Due Wednesday 2015/2/18 1:00pm on Moodle"
output: html_document
---

```{r, echo=FALSE}
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(dplyr))
```

## Example: Delete this section before submitting

```{r}
data(diamonds)
summary(diamonds)
diamonds <- sample_n(diamonds, 1000, replace=FALSE)
```

You can also embed plots, for example:

```{r, echo=FALSE, fig.width=12, fig.height=6}
ggplot(diamonds, aes(x=carat, y=price, color=as.factor(cut))) + geom_point()
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.




## Question 1:

* Plot a "time series" of the number of flights that were delayed by > 30 minutes on each day.  i.e.
    + the x-axis should be some notion of time
    + the y-axis should be the proportion.
* Which seasons did we tend to see the most and least delays of > 30 minutes.

```{r}

```



## Question 2:

I actually prefer flying on older planes.  Even though they aren't as nice, they tend to have more room.  Which airlines should I favor?

```{r}

```



## Question 3:

* What states did listed Southwest Airlines flights tend to fly to?
* What states did all Southwest Airlines flights tend to fly to?

```{r}

```



## Question 4:

What weather patterns are associated with the biggest departure delays?

```{r}

```



## Question 5:

I want to know what proportionately regions (NE, south, west, midwest) each carrier flies to from Houston in the month of July.  Consider the `lubridate` package.

```{r}

```



## Question 6:

Get creative:  Answer one question of your own using this data.  The more interesting the question the better.

```{r}

```
