---
title: "Google Quant Preso"
author: "Albert Y. Kim"
date: "May 27, 2015"
output:
  html_document:
    keep_md: yes
---

```{r, warning=FALSE, message=FALSE, echo=FALSE}
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(knitr))
```



## Abstract

In this presentation I discuss a new data science class taught at Reed College, a small undergraduate-only liberal arts college in Portland, Oregon.  This class was intended for students in any field with a quantitative bent and the only prerequisites were an introductory statistics class and some experience with R.  After describing the background and context that might affect the generalizability of any subsequent discussions, I present my motivations for creating this class and a description of the class' specifics, including my approach to incorporating R and the datasets/statistical topics considered.  More importantly however, I synthesize my experiences and detail how I envision this experience impacting future instances of my introductory statistics classes.  Relatedly, I also propose an idea on how to increase the appeal of statistics to both potential statisticians and non-statisticians alike.  I end with a discussion on my acquired Google wisdom that my students seemed most receptive to. 





## Background and Context

### Myself

* Went to McGill University in math and CS
* Did my PhD in statistics at the University of Washington.
* Worked in Ads Metrics from June 2011 to March 2013.
* Initially took a one year visiting contract at Reed, which got extended to two.
* I'm about to start at Middlebury College in Vermont this fall.  



### Reed College

* Small (1400 students) undergraduate only liberal arts college in Portland, OR
* Established in 1908 because founder
    + Didn't care for sports: no varsity sports, only club teams
    + Despised social clubs: no fraternities
* Smaller classes: the largest class I taught was approx 28 students
* HUGE de-emphasis on grades. Less focus on "doing well on tests", more on "learning"
    + Exams are unproctored
    + Honor principle
    + Students almost **always** apologize before asking anything relating to their grades.
* Obviously lots of variability, but on average students are very motivated and as our President call it, lead "A life of the mind".  
* HIGH degree of interactivity between departments, less segmented than at larger institutions.  Faculty lunch.  The ethos of a liberal arts education.

### Curriculum for All Students

* There is no engineering, business, law school i.e. this is NOT a vocational school.  Somewhat conservative; we still don't have a computer science program and only this past year hired a second computer scientist, although there is now momentum to make this happen.  
* Among the school with the highest proportion of students who go onto to do a PhD.
* All students must complete:
    + a junior qualifying exam
    + a senior thesis
* All incoming Freshmen take Humanities 110 where students read classic texts like the Iliad, Gilgamesh, Ovid
    + part lecture 
    + part **conference**: small discussion sections of 16 students sitting in conference style
* I sat in on a lecture



### Statistics at Reed

* Smaller college so no separate department. Statistics and CS are contained within the math department.
* Typical statistics offerings include
    + Intro stats
    + Year-long junior level probability & mathematical statistics classes
    + Scattering of discipline specific methods classes


### Similar Stuff

* Rachel Schutt did a graduate course at NYU, I'm focusing on undergraduates.








## Motivation for Creating This Class

### Filling Needs

* Many students expressed interest in learning more about statistics after intro stats, but couldn't reorient the Titanic to get to prob/math stats b/c of the prereq structure
* I felt Reed was in need of an applied data analysis class taught by a statistician.
* Initially called it "Case Studies in Statistical Analysis" because I felt the word "Data Science" too buzzwordy.  In retrospect however, I should have.  
* Venn Diagram.  In particular at a liberal arts college


### The Bigger Picture

* ASA president Marie Davidson "Aren't we data science?"
* Institute of Mathematical Statistics (IMS) Bin Yu. 
* UC Davis Prof. Norman Matloff
* Hadley's article
* UMass Amherst:  Data Science Program.  Didn't invite the statisticians



### The Bigger Picture

ASA GAISE Guidelines

1. Emphasize statistical literacy and develop statistical thinking.
2. Use real data.
3. Stress conceptual understanding, rather than mere knowledge of procedures.
4. Foster active learning in the classroom.
5. Use technology for developing conceptual understanding and analyzing data.
6. Use assessments to improve and evaluate student learning.












## Class Description

### Student Profile

* Only prerequisite was intro stats, not so much because of the material, but to ensure students had at least some exposure to using R.
* 18 students
* Various backgrounds, mostly juniors and seniors

```{r, warning=FALSE, message=FALSE, echo=FALSE}
read.csv("MATH_241_S.csv", header=TRUE) %>%
  group_by(major) %>%
  summarise(count=n()) %>%
  arrange(desc(count)) %>%
  kable()
```


### Syllabus

* 60% 6-7 biweekly "mini-reports", varying degree of open-endedness to be submitted in R Markdown format.  Grading and feedback.  
* 35% Term project
* 5% participation


### Class Structure

* Conference model, but with a modern twist.  Most students did bring their own laptops however.  Show photo of ETC 208
    + Students face each other to fascilitate discussion
    + I scouted this room out specifically
* Part lecture, part lab: inject a bit of interactivity/learn by doing.  Having lectures/labs hard split in my intro class was not ideal.  This way I could toy with the mix depending on topic
* Not complete flipped-classroom model


### Principles

* Use real data. i.e. messy as shit.
* Focus on the entire analysis pipeline
* Let the questions/data motivate the statistical methodology, rather than vice-versa.   Inspired by the bottom-up rather than top-down approach that many people in Ads Metrics



### Environment: RStudio

* View the **raw** data
* Easily create R Markdown and Shiny apps
* Navigate files and folders
* Syncs seamlessly with GitHub
* Package management


### Forget Base R

* I remember my 2nd lab in Intro Stats, did stuff with vector indexing.  It was a disaster
* Rich’s [Essay](http://blogs.reed.edu/ed-tech/2015/04/why-should-students-at-a-small-liberal-arts-college-learn-r/).  He learned R from dplyr and ggplot, NOT base R.  He didn’t know how to index elements of a matrix until much later.  Now he had had a consulting site and is now working at Colby College
* R is no longer hard to learn.  Or least the ratio of value/learning data has vastly increased.
    + [Datacamp](https://www.datacamp.com/swirl-r-tutorial)
* Handout cheatsheets


### Data Manipulation

dplyr verbs.  Toolbox graphic 

joining disparate data sets.  HUGE


### Data Visualization

The Grammar of Graphics:


### Datasets

* Houston Flights data
* OkCupid data
* Reed jukebox data:  Talking Heads
* Elections data
* Quandl
* Babynames datasets
* Census data (I love FIPS codes!) joined with health data joined with shapefile data



### Topics

* Regressions, time series, spatial autocorrelation (show image), density plots (prostitution in Portland), text mining, sampling bias, First law of geography
* Jeff Leek’s nature article:  start to finish.  The entire process
* tidy format of data in CSV files.  
* Webscraping using the rvest package
* GitHub and R Markdown for reproducibility
* Good programming practice (Google style guide)
* GitHub for promoting/sharing work
* Shiny apps
* Dates with lubridate
* String manipulation and basic regular expressions with stringr



### Examples:

* Importance of exploratory data analysis
    + Time zones of Reed Jukebox
    + Erroneous join of counties in US
* Miguel's quandl analysis
* Emmeline's thesis




### Student Comments

* Dean’s comment, who was up until then a big STAT user.  
* Jossef's comment, most useful class he's taken at Reed
* 









## Analysis and the Future

### Areas for Improvement

* "I hated that class."  Terrified of statistics and math.  Its interesting to see how its socially less unacceptible to someone say "I'm bad at math", whereas you'd never hear someone say "I'm bad at reading" or "I'm bad at writing".  Not the fault of Reed, this is just prevailing social trends, and Reed is not exempt.
* Statistical topics:  More on dependent data, causal inference, some machine learning (prediction models, overfitting, crossvalidation), missing data
* Database SQL
* Most importantly: ask better questions of the students 


### Flipped Classroom Model

* Follow more of the **flipped-classroom** model where students go over the lectures at home, and use class time.  No one questions that the in person college experience is better, but is it worth $40K a year? 

What value can we add?  Discussions on ambiguities.  Tacit knowledge.  This is where we can add value over MOOC's.  Not as optimistic as Thomas Friedman, as only the hyper-motivated get something out of it.


### Data Visualization

* Lots of people say they don't like stats, almost no one says they don't like data visualization
* Backdoor way to get students interested in statistics (or at least hate it less)
* Data visualization:  The Grammar of Graphics, is a backdoor way to get students interested, or at least, less terrified of statistics.
* Many statistical methods can be summarized visually
* As Roland Pryzbylewski said in Season 4 of The Wire when talking about trying to teach his unruly middle school math class "Trick 'em into thinking they're not learning, and they do."
* Example of Adriana's analysis
* Video game generation (of which I'm part of)


### Data Visualization





### Intro Stats

Backload this material into Intro Stats

* Get them looking at data QUICK
* RStudio, dplyr, and ggplot2 makes this 
* Intro stats:  this is the only stats class they may take
    + de-emphasize probability, hypothesis testing, t-test
    + boost data visualization and regression
* Randomization based methods.  Why?  Students HATE checking conditions for inference.  Tim Hesterberg paper.Introducing permutation tests and boostrapping. 
    + Don't we just get the original sample?  No, sampling with replacement
    + How can that possibly work?
* Better intergration of lectures and labs.  Data science had complete integration, what about larger intro stats class.



### Programming

Big issue, in particular in my intro stats class.  Conflate what they are trying to do with general programming issues [tweet](https://twitter.com/rudeboybert/status/588774930898100224)

* Many students only have experience with point-and-click, nothing on command line.  
* Not even just for-loops.  I used only one for loop this entire class.
    + Thinking algorithmically
    + Parentheses have to match
    + Functions arguments
    + Help files.  Emmeline's stack overflow 
    + You don't necessarily know more, you just get to be a better Googler XKCD comic
    + Debugging
* Formulating a sentence
* If you refer to a variable that you haven't created, then you will get an error
* Like learning a language
* Different students handle frustration differently. Much like a captain barely hanging on to a near mutinuous crew, you need to convince them of its worth.  











## Conclusions

### Google Wisdom Imparted to Students

Presentation on 2011/06/27 given by Dierdre and Amir

* Look at your data ASAP.  Exploratory data analysis.
* Don't thrash
    + Do your due diligence, but don't overdo
    + If you're spinning your wheels, look for and read documentation
    + Seek expert advice!  i.e. come see me!  Reedies have a strong work ethic, but at times it can be to their detriment.  
* You actually don’t know what you are doing until after you have done it.  Do the most braindead thing first, take it end to end, then iterate and improve
* Fighting perfectionist tendencies: think of the marginal return of your efforts:  don't polish the cannonball.
* As analysts:
    + Own the semantics and the significance of the metrics
    + Credibility is all you have, and all you need.  


## Acknowledgements

* Management:  Diane Tang, Amir Najmi, Dierdre O'Brien, Nick Chamandy
* Colleagues:  Ryan Giordano, Jean Steiner, Henning Holdhold, Kathy Zhong
* Others:  Paul Muret, counselor, Victoria Clarke



## Take Home Messages

* R is too hard to learn is no longer an excuse.  The Hadleyverse now make this easier in academia as well.  Even if there, there are deep philosophical principles at work
    + 
* We need to figure out "backdoor ways" to get students interested in statistics.
* Dealing with ambiguity and interpretation is where quantitative analysts, statisticians, data scientists add value.  Unfortunately, this is a process that takes time to develop.  Reed is fortunate in that
    + The class sizes are small, making grading and giving feedback reasonable
    + 21st century conference model to discuss such issues.  
* Interactivity boosts student interest:  burring of lines between lab and lecture.  





## Resources

* Link to GitHub page